### 2018-05-10 Paper/jaccardbaetica.tex
add new lines intro

%primer párrafo más general---- especifico (¿dónde se ha aplicado?)
Material culture is one of the most frequent indicator of trade in the archaeological record. In archaeology, they allow us to highlight a part of mechanism of production and distribution of goods along the Mediterranean \citep{bevan_mediterranean_2014}. Particularly, the spread of those factors have an important impact during the Roman Age, when the progressive exploitation of communication networks allowed the a major interaction between communities \citep{orengo_seeds_2016}. As a result, an important mechanism of production control under Roman government was created spreading by different areas attending to the richness of different places.

@@

Here, therefore, this study proposes an approach to explore the effect of Baetican olive oil production by estimating of similarity index (COPIADO CAMBIAR). The assumption of this analysis is that closer workshops concentrate similar amphoric stamps in a specific area than the farthest workshops. By contrast, if we found similar amphoric stamps in different areas between workshops then the correlation between spatial distance would not be valued.

@@

The chronology in the workshops is widely diverse from the first to the third centuries AD (CITAR). Some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. This could be due to two reasons. First, most of workshops were partially excavated and focused on archaeological surveys in order to collect the maximum stamps as possible. Second, this amphora type was produced during almost three centuries with apparently few changes so they presented a long chronology. (PODRÍA CITARME AQUÍ MUAHA)

@@

The research was funded by European Research Council Advanced Grant EPNet (340828). We are grateful to Simon Carrignon. 
All data has been analysed and conducted in R program version 3.2.4, using vegan package (citar)

>>>>

%primer párrafo más general---- especifico (¿dónde se ha aplicado?)
Material culture is one of the most frequent indicator of trade in the archaeological record. In archaeology, they allow us to highlight a part of mechanism of production and distribution of goods along the Mediterranean \citep{bevan_mediterranean_2014}. Particularly, the spread of those factors have an important impact during the Roman Age, when the progressive exploitation of communication networks allowed a major interaction between communities \citep{orengo_seeds_2016}. As a result, an important mechanism of production control under Roman government was created spreading by different areas attending to the richness of different places.

@@

Here, therefore, this study proposes an approach to explore the effect of Baetican olive oil production by computing of dissimilarity index. The assumption of this analysis is that closer workshops concentrate similar amphoric stamps in a specific area than the farthest workshops. By contrast, if we found similar amphoric stamps in different areas between workshops then the correlation between spatial distance would not be valued.

@@

The chronology in the workshops is widely diverse from the first to the third centuries AD \citep{millet_anforas_1998,rodriguez_baetican_1998,chic2005comercio}. Some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. This could be due to two reasons. First, most of workshops were partially excavated and focused on archaeological surveys in order to collect the maximum stamps as possible. Second, this amphora type was produced during almost three centuries with apparently few changes so they presented a long chronology. (PODRÍA CITARME AQUÍ MUAHA)

@@

The research was funded by European Research Council Advanced Grant EPNet (340828). We are grateful to Simon Carrignon. 
All data has been analysed and conducted in R program version 3.2.4, using the packages \textit{vegan} \citep{oksanen_vegan_2007}.
